Fingerprinting \titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}

### 2018-11-08 paper.tex
Add some keywords
Fix typos and language for fingerprinting overview

\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings

@@

With the amount of information given away from the browser, they can be identified in a stable and mesurable manner \cite{niki:cookie} by emplanting scripts that collect and process those information into the web page, as shown by Nikiforaskis. 
Eckersley from Panopticlick project \cite{panop} demonstrates that browser fingerprinting technology is a fairly effective user tracking tool, drawing attention and usage from many advertising companies. Almost 500K browsers have their information scanned and recorded on the Panopticlick website, and around $83.6\%$ of them can be identified uniquely.
More recently, newer techniques are discovered that exploit the potential issues in JavaScript engine to reveal more information such as operating system and microarchitecture, even hardware information such as screen resolution. \cite{mowery:fg} \cite{boda:user}
As HTML5 and WebGL becomes more popular tools at rendering web sites content, new fingerprinting information is added to the arsenal. More importantly, such fingerprinting information is no longer restricted to browser properties because different hardware and softwares will behave differently when rendering images through the canvas component.\cite{mowery:pixel}

Contrary to the common notion of information leaking, none of the above-mentioned practices involves complicated mechanism such as password hacking, or any sort of attack. This information is just available.
The underlying reason that so much fine-grained information about the browser and the user can be retrieved is the necessity for a web application to be able to render the pages based on differnt devices effectively. Responsive web application needs to know the dimension of the screen; a video application might need to know the presence of plugin like Adobe Flash. 
In order to serve various demands, the browser expose APIs for developers to query such information, e.g., the built-in \verb|navigator| and \verb|screen| objects from Javascript which reveals the browser name, version, platform information. 
In addition, browser plugins, softwares from third-party which add in many enriching features to the browser have access to information about the computers, that can expose more accurate identifiers.

>>>>

\keywords{Authentication, device fingerprinting, web authentication} % NOT required for Proceedings

@@

With the amount of information given away from the browser, they can be identified in a stable and mesurable manner \cite{niki:cookie} by emplanting scripts that collect and process those information into the web page, as shown by Nikiforaskis. 
Eckersley from the Panopticlick project \cite{panop} demonstrates that browser fingerprinting technology is a fairly effective user tracking tool, drawing attention and usage from many advertising companies. Almost 500K browsers have their information scanned and recorded on the Panopticlick website, and around $83.6\%$ of them can be identified uniquely.
More recently, newer techniques have been discovered that use JavaScript to reveal more information such as operating system and microarchitecture, and even hardware information such as screen resolution. \cite{mowery:fg} \cite{boda:user}
As HTML5 and WebGL becomes more popular tools for websites, new sources of fingerprinting information is added to the arsenal. More importantly, such fingerprinting information is no longer restricted to browser properties because different system configurations will behave differently when rendering images through the canvas component.\cite{mowery:pixel}

Contrary to the common notion of information leaking, none of the above-mentioned practices involves complicated mechanisms such as password hacking, or any sort of attack. The is because so much fine-grained information about the browser and the user can be retrieved as a necessity for web applications to be able to serve content based on different devices effectively. For example, responsive web applications need to know the dimension of the screen, while a video streaming service may need to know the presence of plugins like Adobe Flash. 
In order to serve these various demands, the browser expose APIs for developers to query such information, e.g., the built-in \verb|navigator| and \verb|screen| objects in JavaScript which reveal the browser name, version, platform information. 
In addition, browser plugins which add  features to the browser also have access to information about the computer that can expose more accurate identifiers.
